%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{
\end{itemize}}
\newcommand{\resumeItemListStart}{
\begin{itemize}}
    \newcommand{\resumeItemListEnd}{
\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
  \textbf{\Huge \scshape Josué Amador-Rojas}
\end{center}

%-----------Contact-----------
\begin{center}
  % \small (506) 7201-1545 $|$
  \small San José $|$
  \href{tel:+50672011545}{\underline{(506) 7201-1545}} $|$
  \href{mailto:bjamadorr@gmail.com}{\underline{bjamadorr@gmail.com}} $|$
  \href{https://www.linkedin.com/in/rodamaj}{\underline{linkedin.com/in/rodamaj}} $|$
  \href{https://rodamaj.github.io}{\underline{rodamaj.github.io}}
\end{center}

%-----------Summary-----------
\section{Summary}

Software Engineer and Computer Science student with 6+ years of experience designing and building mobile, web, and backend systems. Experienced in software architecture, scalable application development, and cross-platform solutions. Currently expanding expertise in computer science fundamentals, including optimization, artificial intelligence, algorithms, and analytical problem solving.

%-----------Professional Experience-----------
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Konrad Group}{Cartago, CR}
{Mobile \& Backend Developer}{Jan 2022 -- Jul 2025}
\resumeItemListStart
    \resumeItem{Designed and maintained mobile, web, and backend solutions for clients across multiple industries.}
    \resumeItem{Developed scalable backend services and APIs using Java, Spring Boot, Redis, and relational databases.}
    \resumeItem{Built cross-platform and native mobile applications with Flutter, Kotlin, and modern Android frameworks.}
    \resumeItem{Applied reactive programming principles to support real-time and event-driven workflows.}
    \resumeItem{Collaborated in cross-functional teams and contributed throughout the software development lifecycle, from architecture to deployment.}
\resumeItemListEnd

% \resumeSubheading
% {Correos de Costa Rica}{San José, CR}
% {Bilingual Customer Service Representative}{Mar 2017 -- Jan 2018}
% \resumeItemListStart
% \resumeItem{Provided bilingual customer support (phone, email, chat) for banking-related services.}
% \resumeItem{Ensured effective communication and issue resolution in both English and Spanish.}
% \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Academic Experience-----------
\section{Academic Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Universidad de Costa Rica}{San José, CR}
{Teaching Assistant}{Mar 2019 -- Present}
\resumeItemListStart
    \resumeItem{Supported undergraduate courses in programming, software engineering, and mathematics through lectures, labs, grading, and student mentoring across more than 10 course offerings.}
\resumeItemListEnd
\resumeSubheading
{Universidad de Costa Rica}{San José, CR}
{Frontend Developer, Intern}{Aug 2021 -- Dec 2021}
\resumeItemListStart
    \resumeItem{Built a real-time delivery SPA with Angular and Firebase.}
    \resumeItem{Collaborated with UI/UX designers and set up CI with GitHub Actions.}
\resumeItemListEnd
\resumeSubheading
{Universidad de Costa Rica}{San José, CR}
{Mobile Developer, R\&D}{Jul 2020 -- Jan 2021}
\resumeItemListStart
    \resumeItem{Created a COVID-19 checklist app with Flutter and Firebase for symptom tracking.}
    \resumeItem{Used Clean Architecture and BLoC for scalable, testable code.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Education-----------
\section{Education}

\resumeSubHeadingListStart

\resumeSubheading
{Universidad de Costa Rica}{San José, CR}
{Bachelor of Science, Computer Science}{Aug 2025 -- Present}

\resumeItemListStart
    \resumeItem{Relevant coursework: Optimization, Artificial Intelligence, Computer Architecture, Computability and Complexity, Differential Equations}
\resumeItemListEnd

\resumeSubheading
{Universidad de Costa Rica}{San José, CR}
{Bachelor of Science, Software Engineering}{Mar 2018 -- Dec 2021}

\resumeItemListStart
    \resumeItem{Highest GPA Award, Software Engineering (GPA 3.95/4.00), June 2020}
    \resumeItem{Highest GPA Award, Engineering Field (GPA 3.95/4.00), June 2020}
\resumeItemListEnd

% \resumeSubheading
% {CTP Vázquez de Coronado}{San José, CR}
% {Associate Degree, Customer Service}{Feb 2014 -- Dec 2016}
\resumeSubHeadingListEnd

%-----------Certifications-----------
\section{Certification}
\resumeSubHeadingListStart
\resumeSubheading
{Oracle Certified Professional: Java SE 17 Developer}{}
{Oracle}{Issued Nov 2023}
\resumeSubHeadingListEnd

%-----------Tech Stack-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item{
        \vspace{1mm}
        \textbf{Languages}: Java, Kotlin, Dart, TypeScript, Python, SQL, MATLAB \\
        \textbf{Software Engineering}: Backend Development, Mobile Development, REST APIs, Software Architecture \\
        \textbf{Frameworks \& Platforms}: Spring Boot, Flutter, Android Jetpack, Angular, Vue, SwiftUI \\
        \textbf{Computer Science}: Optimization, Artificial Intelligence, Algorithms, Experimental Design \\
        \textbf{Tools}: Git, Azure DevOps, GitLab CI/CD
    }}
\end{itemize}

%-----------Awards-----------
% \section{Awards}
%     \resumeSubHeadingListStart
%       \resumeSubheading
%         {Universidad de Costa Rica}{}
%         {Highest GPA Award, Software Engineering, GPA: 9.88}{June 2020}
%       \resumeSubheading
%         {Universidad de Costa Rica}{}
%         {Highest GPA Award, Engineering Field, GPA: 9.88}{June 2020}
%     \resumeSubHeadingListEnd

\end{document}
